Trajectories

### 2023-02-16 docs/index.qmd
Update report (still not functional) @

---
title: "Trajectories"
subtitle: "Lab notes"
date: "Updated: `r format(Sys.Date(), '%Y/%m/%d')`"
authors:
  - name: Gonzalo Garcia-Castro
    orcid: 0000-0002-8553-4209
    email: gonzalo.garciadecastro@upf.edu
    corresponding: true
    affiliations:
      - name: Universitat Pompeu Fabra
        department: Center for Brain and Cognition
        address: Ramon Trias fargas 25-27
        city: Barcelona
        state: Spain
        postal-code: 08005
  - name: Daniela S. Ávila-Varela
    orcid: 0000-0002-3518-8117
    affiliations:
      - name: Universitat Pompeu Fabra
        department: Center for Brain and Cognition
  - name: Ignacio Castillejo
    orcid: 0000-0001-7445-0416
    affiliations:
      - name: Universidad Autónoma de Madrid
        department: Departamento de Psicología
  - name: Nuria Sebastian-Galles
    orcid: 0000-0001-6938-2498
    affiliations:
      - name: Universitat Pompeu Fabra
        department: Center for Brain and Cognition
abstract: "Bilinguals face the challenging task of learning words from languages with overlapping phonologies. Floccia et al. (2018) reported larger vocabulary sizes for 24-month-old bilinguals that were learning languages that shared a greater amount of cognates (e.g., English-Dutch). The mechanisms underlying this effect remain unknown. We explore two compatible scenarios. First, we test whether cognates are learnt earlier than non-cognates. This would account for the difference in vocabulary size associated to the amount of shared cognates across languages. Second, we explore the possibility that the word-forms of one language interact with those in the other language, scaffolding the acquisition of their translation equivalents when their phonologies overlap. This mechanism, in line with the parallel activation account of bilingual speech perception, would provide a plausible explanation to why cognates are acquired ealier by bilinguals. We developed an online tool to collect parental reports of receptive and productive vocabularies from children learning Catalan and/or Spanish, and present data on receptive and productive vocabulary of bilingual toddlers aged 12 to 34 months."
format:
    html:
        code-copy: hover
        reference-location: margin
        code-overflow: scroll
link-external-newwindow: true
code-fold: true
code-line-numbers: true
fig-dpi: 1000
page-layout: full
warning: false
echo: false
toc: true
colorlinks: true
number-sections: true
bibliography: "references.bib"
csl: "apa7.csl"
---

@@

# load targets as R objects
tar_load(participants)
tar_load(responses)
tar_load(items)
tar_load(bvq_data)
tar_load(model_fit_0)
tar_load(model_fit_1)
tar_load(model_fit_2)
tar_load(model_fit_3)
tar_load(model_fit_4)
tar_load(model_fit_4_prior)
tar_load(model_fit_prior)
tar_load(model_loos)
tar_load(posterior_draws)
tar_load(posterior_draws_re)

>>>>

---
title: "Trajectories"
subtitle: "Lab notes"
date: "Updated: `r format(Sys.Date(), '%Y/%m/%d')`"
authors:
  - name: Gonzalo Garcia-Castro
    orcid: 0000-0002-8553-4209
    email: gonzalo.garciadecastro@upf.edu
    corresponding: true
    affiliations:
      - name: Universitat Pompeu Fabra
        department: Center for Brain and Cognition
        address: Ramon Trias fargas 25-27
        city: Barcelona
        state: Spain
        postal-code: 08005
  - name: Daniela S. Ávila-Varela
    orcid: 0000-0002-3518-8117
    affiliations:
      - name: Universitat Pompeu Fabra
        department: Center for Brain and Cognition
  - name: Ignacio Castillejo
    orcid: 0000-0001-7445-0416
    affiliations:
      - name: Universidad Autónoma de Madrid
        department: Departamento de Psicología
  - name: Nuria Sebastian-Galles
    orcid: 0000-0001-6938-2498
    affiliations:
      - name: Universitat Pompeu Fabra
        department: Center for Brain and Cognition
abstract: "Bilinguals face the challenging task of learning words from languages with overlapping phonologies. Floccia et al. (2018) reported larger vocabulary sizes for 24-month-old bilinguals that were learning languages that shared a greater amount of cognates (e.g., English-Dutch). The mechanisms underlying this effect remain unknown. We explore two compatible scenarios. First, we test whether cognates are learnt earlier than non-cognates. This would account for the difference in vocabulary size associated to the amount of shared cognates across languages. Second, we explore the possibility that the word-forms of one language interact with those in the other language, scaffolding the acquisition of their translation equivalents when their phonologies overlap. This mechanism, in line with the parallel activation account of bilingual speech perception, would provide a plausible explanation to why cognates are acquired ealier by bilinguals. We developed an online tool to collect parental reports of receptive and productive vocabularies from children learning Catalan and/or Spanish, and present data on receptive and productive vocabulary of bilingual toddlers aged 12 to 34 months."
format:
    html:
        code-copy: hover
        reference-location: margin
        code-overflow: scroll
link-external-newwindow: true
code-fold: true
code-line-numbers: true
fig-dpi: 1000
page-layout: full
warning: false
echo: false
toc: true
colorlinks: true
number-sections: true
csl: "../assets/apa7.csl"
bibliography: "../assets/references.bib"
---

@@

# load targets as R objects
tar_load(participants)
tar_load(responses)
tar_load(items)
tar_load(bvq_data)
tar_load(model_fit_0)
tar_load(model_fit_1)
tar_load(model_fit_2)
tar_load(model_fit_3)
tar_load(model_fit_4)
tar_load(model_fit_4_prior)
tar_load(model_fit_prior)
tar_load(model_loos)
tar_load(posterior_draws)
tar_load(posterior_draws_re)
tar_load(marginal_effects_epreds)
